Domain-Driven, Generative Data Model for BigPetStore

### 2014-07-18 bdcloud_paper/latex/paper.tex
Added description of customre locations and pets

Store records contain a unique identifier and a location in the form of a 5-digit zip code.  The locations of the stores are modeled by a PDF that gives the probability that a store's location is the given zip code. We designed the PDF to give to zip codes in high-population, high-income areas the highest probabilities. The PDF is composed of two individual PMFs. One PMF determines the probability of each zip code as the population of that zip code over the total population:

@@

The stores' locations are generated by sampling zip codes from the PDF.  A variety of methods can be used such as Roulette Wheel sampling and Monte Carlo methods.

@@

The customers’ locations are modeled so that customers are placed within  The customer location is modeled as an exponential distribution over the distance to the nearest store.

[discuss parameters used in later sections, methods for setting number of customers per store]

>>>>

Store records contain a unique identifier and a location in the form of a 5-digit zip code.  The locations of the stores are modeled by a probability density function (PDF) that gives the probability that a store's location is the given zip code. We designed the PDF to give to zip codes in high-population, high-income areas the highest probabilities. The PDF is composed of two individual PDFs. One PDF determines the probability of each zip code as the population of that zip code over the total population:

@@

The stores' locations are generated by sampling zip codes from the PDF using a Roulette Wheel sampler.

@@

\textcolor{red}{names}

For each proposed customer location zipcode $z$, we compute the distance between $z$ and every store's zipcode to find the closest store.  We compute the distance $d$ between $z$ and the zipcode $s_z$ of the closest store.  The weight $w_z$ for each zipcode $z$ is modeled using an exponential distribution with the average distance $\beta$.

\begin{align}
&w_z = \beta^{-1} \exp(-\beta^{-1} \, d_m(z)) \\
&d_m(z) = \min_{s_z} \, d(z, s_z) \nonumber
\end{align}

To find the probabilities, the weights are normalized:

\begin{align}
&p(\text{location} = \text{z}) = W^{-1} w_z \\
&W = \sum_{z} w(z) \nonumber
\end{align}

The customer locations are sampled from the PDF using a Roulette Wheel sampler.

We determine the number of pets $N_p$ each customer has by sampling from a uniform distribution of integers. We then sample the number of dogs $N_d$ as a uniform distribution between 0 and $N_p$.  The remaining number of pets are assigned to be cats.

\begin{align}
N_p \sim U(1, b) \\
N_d \sim U(0, N_p) \nonumber \\
N_c = N_p - N_d \nonumber
\end{align}
